%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\publicationItem}[2]{
    \item\small{
      \textbf{#1}{ #2 \vspace{-2pt}}
    }
  }

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingJobPosition}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} - #5 & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%-------------------------
% Variables

\newcommand{\name}{David Torres}
\newcommand{\website}{https://www.linkedin.com/in/datorres/}
\newcommand{\email}{torresdavid@gmail.com}
\newcommand{\phone}{+1-512-825-5339}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{\website}{\Large \name}} & Email : \href{mailto:\email}{\email}\\
  \href{\website}{\website} & Mobile : \phone \\
   & San Diego, CA\\
\end{tabular*}

%-----------Programming skills -----------------
\section{Development Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages}{: C\#, SQL, Go, Ruby, C/C++, JavaScript, Python, R, Java, Bash, Zsh, Powershell}        
  }
  \item{    
    \textbf{Technologies}{: AWS, Azure, Docker, MySQL, SQL Server, .NETCore, REST, TypeScript, Linux, Windows, 
    Real Time OSes, Git, XAML/MVVM, WebRTC, ML, Computer Vision}
  }
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California at San Diego}{San Diego, CA}
      {Master of Science in Computer Science (machine learning program)}{2004 -- 2009}
    \resumeSubheading
      {University of Texas at Austin}{Austin, TX}
      {Bachelor's of Science in Computer Science}{1999 -- 2004}
    \resumeSubheading
    {University of Texas at Austin}{Austin, TX}
    {Bachelor's of Science in Mathematics (scientific computation program)}{1999 -- 2004}
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    % --- REFLEXION HEALTH ---
    \resumeSubheadingJobPosition
        {Reflexion Health}{San Diego, CA}
        {Principal Software Engineer}{Jan 2019 - Mar 2020}
        {A Gamified Teletherapy Company}
        \resumeSubSubheading
        {Lead Software Engineer}{Mar 2017 - Jan 2019}
        \resumeItemListStart
            \resumeItem{
                Managed a team of up to 5 engineers and 6 off-shore consultants to develop our HIPAA regulated production services.
                Released a major redesign of our product followed by quarterly releases.
            }
            \resumeItem{
                Performed hands-on supervision of web app, backend and database development. Performed architecture, technical project management, 
                implementation and bug fixing. (C\#, Rails, Go, JavaScript, MySQL)  
            }
            \resumeItem{
                Architected, implemented, and project managed a 2-year long initiative to create a multi-tenant backend and migrate customer data. This enables 
                steamlined management of patients and clients, will lead to a cost savings of 65\% over the legacy infrastructure, and reduces the client
                on-boarding time from several weeks to down to zero.
            }
             \resumeItem{
                Oversaw the architecture and implementation of our data-analytics backend consisting of our data processing pipelines and 
                reporting services that management used to make informed and timely business decisions.
            }
            \resumeItem{
                Contributed to the continuous improvement of the SDLC for my team by implementing containerized local development workflows, building automation and tooling, and 
                driving agile-based process improvements.
            }
        \resumeItemListEnd
            
      
    % --- SIGNAL GENETICS ---
    \resumeSubheadingJobPosition
        {Signal Genetics}{Carlsbad, CA}
        {Principal Software Engineer}{Jan 2015 - Feb 2017}
        {A Diagnostics Biotech Company}
        \resumeItemListStart
            
            \resumeItem{                
                Founded the company's development team, managing 2 engineers and 2 consultants to develop the company's information
                processing infrastructure.
            }

            \resumeItem{
                Designed a cloud-based microservice pipeline to process our test results.(Azure, Service Bus, Web Apps, Blob Storage.)
            }

            \resumeItem{
                Developed a web app that allowed us to dramatically increase billing velocity. 
                (AngularJS, MVC, WebAPI)
            }

            \resumeItem{
                Developed REST APIs to interface with vendor systems to automate the collection of operational telemetry.
            }           

            \resumeItem{
                Drove adoption of  software engineering best practices such as unit testing, CI, Git Flow and controlled release procedures.                
            }

            \resumeItem{
                Managed consultants and vendors to maintain and extend the company's Lab Information System.
            }

            \resumeItem{
                Developed formal software control policies and procedures to conform to SOX and HIPAA.
            }

        \resumeItemListEnd

    % --- ANSSUR ---
        \resumeSubheadingJobPosition            
            {Anssur Corp.}{San Diego, CA}
            {Software Engineer/Consultant}{July 2009 - Dec 2015}
            {Analytics and Robotics Consulting (various companies)}

            \resumeItemListStart
                \resumeItem{Developed machine learning algorithms to detect traffic signs and traffic signals captured by camera-equipped field vehicles. 
                Developed an SVM classifier architecture trained on HoG image features. Evaluated Viola-Jones based boosting classifiers. 
                Developed custom software to generate labeled training data. (C\#, XAML, R, OpenCV, EmguCV)
                }

                \resumeItem{Developed software to control a minimally-invasive surgical robot: Designed and implemented a global, event-based state-handling 
                framework to handle all sensor interactions (C++, Windows real-time OS, EtherCAT.) Also developed a
                TCP/UDP based presentation framework that interfaced our real-time software with a tablet UI. (C\#, XAML, MVVM)
                }

                \resumeItem{Developed software for a specialized stethoscope for use in telemedicine applications. Software streams PCM audio 
                across the internet to a desktop client. Performs up-sampling and down-sampling on PCM audio. Developed audio buffering algorithms
                for internet transmission, including audio quality-of-service detection and audio error-correction (packet loss concealment.) 
                (C++, DirectSound API, MFC)
                }

                \resumeItem{Full stack development of a flash-based analytics dashboard to visualize and analyze company-wide operational and sales data. 
                (Adobe Flash/AIR, Apache Tomcat, Java, SQL Server)
                }

                \resumeItem{Developed software to rapidly prototype, visualize and profile image processing algorithms. Implemented
                Otsu based thresholding to detect embryoid bodies in medical images.
                }

            \resumeItemListEnd

    % --- VISION ROBOTICS  ---
        \resumeSubheadingJobPosition
             {Vision Robotics}{San Diego, CA}
             {Software Engineer}{Apr 2008 - Jun 2009}
             {Computer Vision and Robotics Company}

            \resumeItemListStart
                \resumeItem{Developed stereo image pair 3D reconstruction algorithms for use in robotic obstacle avoidance. 
                    Implemented correlation based pixel matching methods and stereopsis for use in a robotic grapevine pruner
                    and robotic apple picker. (C/C++)}
                
                \resumeItem{Developed algorithms for detecting, tracking and performing 3D reconstruction of grapevine anatomy 
                across a time series of moving stereo pair images. Employed edge detection, watershed based skeletonization, Hough line transforms.}
                
                \resumeItem{Developed fast image interest point detection libraries based on Harris and Moravec corner detection algorithms.}
                
                \resumeItem{Investigated and developed object recognition methods for use in fruit detection. 
                    Employed SVM and nearest neighbor classification techniques on SIFT-based bag-of-visual-words features for feasibility analysis.}
                
                \resumeItem{Conducted research of fruit color-space properties to improve color based object detection. 
                    Employed GMM analysis on RGB and HSV color spaces to derive an efficient threshold based classification algorithm.}
                
                \resumeItem{(See video: \href{http://www.youtube.com/watch?v=9GaGO9LIDEA}{http://www.youtube.com/watch?v=9GaGO9LIDEA})}
            \resumeItemListEnd

    % --- UCSD RESEARCH ASSISTANT   ---
        \resumeSubheading
        {University of California at San Diego}{San Diego, CA}
        {Graduate Research Assistant}{May 2006 - May 2009}        

        \resumeItemListStart
            \resumeItem{Conducted research on unsupervised machine learning methods to recognize musically meaningful words from a data set 
                of audio and text annotations. Implemented a novel algorithm, Sparse CCA, to explore correlations between audio and text.
                Used convex optimization packages SeDuMi, CVX, Mosek.}
            \resumeItem{Helped develop a music auto-tagging and keyword search engine. Involved GMM analysis of audio features and text using
                advanced EM methods (Mixture Hierarchies EM) to deal with large datasets.}

            \resumeItem{Worked with team to develop software pipeline to analyze music and interface with web-facing database. 
            Worked on software to interact with data base, perform audio feature extraction, and perform GMM analysis. (Java, PHP and MySQL)}

            \resumeItem{Published several articles based on research.}

        \resumeItemListEnd

    
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------    
  \resumeSubHeadingListEnd


%-----------Publications-----------------
\section{Publications}

    \resumeItemListStart
  
    \publicationItem{Using Sparse CCA for Vocabulary Selection.}
        {Masters Thesis, Univ. of California at San Diego (2009).}
    
    \publicationItem{Semantic Annotation and Retrieval of Music and Sound Effects.}
        {IEEE Transactions on Audio, Speech and Language Processing, Volume: 16, Issue 2.
    Douglas Turnbull, Luke Barrington, David Torres, and Gert Lanckriet (2008).}

    \publicationItem{Finding Musically Meaningful Words by Sparse CCA.}
        {Neural Information Processing Systems (NIPS) Workshop on Music, the Brain and Cognition. David Torres, Bharath K.
    Sriperumbudur, and Gert Lanckriet (2007).}

    \publicationItem{Sparse Eigen Methods by D.C. Programming.}
        {ICML, International Conference on Machine Learning. Bharath K. Sriperumbudur, David Torres and Gert Lanckriet (2007).}

    \publicationItem{Identifying Words that are Musically Meaningful.}
        {ISMIR, International Conference on Music Information Retrieval. David Torres, Douglas Turnbull, Luke Barrington and Gert
    Lanckriet (2007).}

    \publicationItem{Towards Musical Query-by-Semantic Description using the CAL500 Data Set.}
        {SIGIR, Special Interest Research Group on Information Retrieval. Douglas Turnbull, Luke
    Barrington, David Torres and Gert Lanckriet (2007).}

    \publicationItem{Semantic Similarity for Music Retrieval.}
        {Music Information Retrieval Evaluation Exchange (MIREX). Audio Music Similarity Task - 3rd Place (no statistically significant
    Difference between top 4 teams). Luke Barrington, Douglas Turnbull, David Torres, Gert Lanckriet
    (2007).}

    \publicationItem{Modeling the Semantics of Sound.}
        {NIPS Workshop on Advances in Models for Acoustic Processing. Douglas Turnbull, Luke Barrington, David Torres, Gert Lanckriet (2006).}
  
    \resumeItemListEnd


%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, JavaScript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}